ECCCos from the Black Box:\\ Faithful Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-09-27 paper/tables.Rmd

```{r}
dt <- lapply(files[sapply(files, function(x) grepl("generator_params.csv",x))], function(x) {
    fread(file.path(paste0(res_path,"params"), x))
})
dt <- Reduce(function(x,y) {rbind(x,y, fill=TRUE)}, dt)
dt <- dt[,.(dataname,eta,lambda_1,lambda_2,lambda_3)]
dt[,dataname:=factor(dataname, levels=dataset_order)]
dt <- dt[order(dataname)]
col_names <- c(
  "Dataset",
  "$\\eta$", "$\\lambda_1$", "$\\lambda_2$", "$\\lambda_3$"
)
kbl(
  dt, caption = "Generator hyperparameters. \\label{tab:genparams} \\newline", 
  align = "r", col.names=col_names, booktabs = T, escape=F, 
  format="latex", linesep = ""
) %>%
  kable_styling(font_size = 8) %>%
  kable_paper(full_width = F) %>%
  save_kable("paper/contents/table_gen_params.tex")
```

>>>>

```{r}
dt <- lapply(files[sapply(files, function(x) grepl("generator_params.csv",x))], function(x) {
    fread(file.path(paste0(res_path,"params"), x))
})
dt <- Reduce(function(x,y) {rbind(x,y, fill=TRUE)}, dt)
dt[is.na(reg_strength),reg_strength:=0]
dt <- dt[,.(dataname,eta,lambda_1_Δ,lambda_2_Δ,lambda_3_Δ,reg_strength)]
dt[,dataname:=factor(dataname, levels=dataset_order)]
dt <- dt[order(dataname)]
col_names <- c(
  "Dataset",
  "$\\eta$", "$\\lambda_1$", "$\\lambda_2$", "$\\lambda_3$", "Ridge penalty"
)
kbl(
  dt, caption = "Generator hyperparameters: the optimiser step size ($\\eta$); penalty strengths where $\\lambda_1$ applies to all generators but \\textit{Schut} and the other parameter are specific to \\textit{ECCCo}; finally, the strength for the Ridge penalty on energy for \\textit{ECCCo}.\\label{tab:genparams} \\newline", 
  align = "r", col.names=col_names, booktabs = T, escape=F, 
  format="latex", linesep = ""
) %>%
  kable_styling(font_size = 8) %>%
  kable_paper(full_width = F) %>%
  save_kable("paper/contents/table_gen_params.tex")
```
